Open-Vocabulary Semantic Parsing\\with both Distributional Statistics and Formal Knowledge

### 2016-03-18 papers/acl2016/paper.tex
Getting close...
Former-commit-id: c27e7319ef51ed8cff9c6d7725164f8ac171482d

\title{Combining Formal and Distributional Models of Predicate Semantics}

@@

  We consider the problem of learning models of predicate (category and
  relation) semantics using both distributional information and structured
  information contained in a formal knowledge base.  Most previous approaches
  to modeling predicate semantics have either been purely distributional (such
  as word2vec and knowledge base embedding methods) or purely formal (such as
  most semantic parsers).  Distributional approaches have very broad coverage,
  but lack the compositional, logical semantics used by semantic parsers, and
  it has so far been difficult to combine the benefits of both of these
  techniques.

  In this paper, we present a method that incorporates logical statements
  derived from a knowledge base into distributional models of categories and
  relations.  Instead of mapping a phrase to a single logical statement, as
  done by semantic parsers, our method uses logical statements as features
  added to distributional models of words, allowing the model to learn that
  Freebase entities that are "honchos" are people, not buildings, and that they
  are frequently CEOs or film producers.  We use these models in an
  open-vocabulary semantic parsing task, showing a 62\% relative improvement in
  mean average precision over a distributional-only model.

@@

How should a computer program represent the meaning of a word or a
phrase? Recent work has suggested two vastly different
approaches---distributional vector space models and semantic
parsing---each with its own advantages and disadvantages. On one hand,
distributional models produce a vector representation of the meaning
of each word from a large unlabeled text corpus. These models have
broad coverage but a shallow semantics centered around word
similarity. On the other hand, semantic parsing translates natural
language into logical queries against a formal knowledge base, such as
Freebase. This approach produces a rich compositional semantics and
furthermore can leverage structured information from the knowledge
base, e.g., to answer natural language questions. However, semantic
parsers have limited coverage as they can only represent the meanings
of words that can be mapped to knowledge base predicates. A critical
question is \emph{how do we obtain the benefits of both approaches?}

\begin{figure*}[ht]
  \small
  \begin{minipage}{0.28\linewidth}
    \textbf{Input Text}\\Italian architect \blank{}
  \end{minipage}
%
  ~~ $\rightarrow$ ~~~~~~
%
  \begin{minipage}{0.7\linewidth}
    \textbf{Logical Form}\\
    $\lexicalpredicate{architect}(x)~\land~\lexicalpredicate{architect\_N/N}(\entity{Italy}, x)$
  \end{minipage}

@@

In this work, we introduce new models of predicate semantics that
leverage both structured information from Freebase and distributional
information. Our key observation is that, while there is no Freebase
predicate that corresponds exactly to the meaning of ``honcho,''
Freebase \emph{does} contain predicates that \emph{partially}
represent its meaning. For example, an entity that can be called
``honcho'' is likely to have type \formalpredicate{person}. We therefore
incorporate \emph{features} based on Freebase paths into the predicate
models of K\&M and learn per-predicate weights for these features
using distributional information (\figref{overview}). This approach
effectively learns the meaning of a word as a distributional vector
plus a \emph{weighted combination of Freebase queries}, a considerably
more expressive representation than either existing semantic parsers
or K\&M.

We demonstrate our approach on the task of answering fill-in-the-blank
natural language queries, finding that our approach provides a 62\%
relative improvement in mean average precision over K\&M. (TODO: other
empirical findings? It would be nice to talk about what features get
learned for what words, etc.)

@@

In this work, we make heavy use of the open-vocabulary semantic parser
of Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, as
well as features derived from a knowledge base using a technique
called subgraph feature extraction~\cite[SFE]{gardner-2015-sfe}.
Accordingly, in this section we briefly describe both of these
techniques.

@@

Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
introduced a technique for learning semantic parsers with open
predicate vocabularies (hereafter referred to as K\&M). Instead of
mapping text directly to Freebase queries, this method parses text to
a surface logical form whose predicates are derived directly from the
words in the text. Next, a distribution over denotations for each
predicate is learned using a matrix factorization approach similar to
that of Riedel et
al.~\shortcite{riedel-2013-mf-universal-schema}. This distribution is
concisely represented using a probabilistic database, which also
enables efficient probabilistic execution of logical form queries.

The truth probability of a predicate instance such as
\lexicalpredicate{architect}(\entity{AndreaPalladio}) is learned using
probabilistic matrix factorization. This factorization has two sets of
parameters: each category or relation has a learned $k$-dimensional
embedding $\theta$, and each entity or entity pair has a learned
embedding $\phi$. The probability assigned to a category instance
$c(e)$ or relation instance $r(e_1, e_2)$ is given by:

@@

This paper extends K\&M by modifying the models of predicate semantics
as described in \secref{method}. K\&M introduced several variations of
their parser; in this work, we use their query ranking objective, as
it had the best performance, and we compare against the model they
called ``Factorization,'' without ensembling it with a corpus lookup
baseline.

@@

    \path[]
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{nationality}} (2)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (3)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{designed}} (5)
      (2) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (4)
      (5) edge node [sloped, anchor=center, above] {\formalpredicate{located\_in}} (2);
  \end{tikzpicture}
  }
  \textbf{Features between \entity{Palladio} and \entity{Italy}}:\\
  \textless\formalpredicate{nationality}\textgreater\\
  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater
  \caption{A subset of the Freebase graph, and some example extracted features
  between \entity{Palladio} and \entity{Italy}.  The actual Freebase relations
  and entity identifiers used are modified here to aid readability.}
  \label{fig:sfe}
\end{figure}

Subgraph feature extraction (SFE) is a technique introduced by Gardner and
Mitchell~\shortcite{gardner-2015-sfe} for generating feature matrices over node
pairs in a graph with labeled edges.  Given a pair of nodes in a graph, SFE
performs a search to characterize a subgraph around those two nodes, then
extracts various kinds of features from that subgraph, such as the set of edge
sequences that connect the two nodes.  \figref{sfe} shows an example subgraph,
centered around \entity{Andrea Pallado} and \entity{Italy}, and features that
would be extracted for that entity pair.  Gardner and Mitchell used these
features to perform link prediction in the graph, using characteristics of the
subgraph around two nodes to determine if an edge of a particular type should
exist between those nodes.\footnote{When the graph corresponds to a knowledge
base like Freebase, this task is also known as knowledge base completion.}
Gardner and Mitchell only used these features to model formal KB relations,
however.

We differ from the work done by Gardner and Mitchell in two ways.  First, we
apply these features to models of natural language, instead of formal KB
relations.  There are some non-trivial problems that need to be solved in order
to make this work, which will be discussed in \secref{method}.  Second, Gardner
and Mitchell only considered generating feature matrices over node \emph{pairs}
in a graph, with which one can model binary relations.  The natural language
queries we wish to answer also involve unary predicates, or categories.  We
thus extend SFE to also generate feature matrices over \emph{nodes} in a graph,
an extension that is straightforward and is also discussed in more detail in
\secref{method}.

@@

We evaluate our models of predicate semantics on a fill-in-the-blank
natural language query task.  Each test example is a natural language
phrase containing at least two Freebase entities, one of which is held
out.  The system must propose Freebase entities to fill in the blank
left by the held out entity, and the predicted entities are then
judged manually for correctness.  We compare our proposed models,
which combine distributional and formal elements, with a
distributional-only baseline from prior work.  All of the data and
code used in these experiments is available at [url withheld for
review].

@@

We also used the test set created by Krishnamurthy and Mitchell, which
contains 220 queries generated in the same fashion as the training
data from a separate section of ClueWeb.  However, as they did not
release a development set in with their data, we used this set as a
development set.  For a final evaluation, we generated another,
similar test set from a different held out section of ClueWeb, in the
same fashion as done by Krishnamurthy and Mitchell.  This final test
set contains 307 queries.  We report results on both of these test
sets below.

@@

We compare three models in our experiments: (1) a distributional-only
model (the prior work of Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}); (2)
a formal-only model (new to this work), where the distributional
parameters $\theta$ and $\phi$ in \secref{formal-and-distributional}
are fixed at zero; and (3) the combined model described in
\secref{formal-and-distributional} (also new to this work).  Except
where noted, all experiments use our modified logical forms
(\secref{better-lfs}) and our entity proposal mechanism
(\secref{better-candidates}).

@@

Given a fill-in-the-blank query such as ``Italian architect
\blank{}'', each system produces a ranked list of 100 candidate
entities.  To compare the output of the systems, we follow a pooled
evaluation protocol commonly used in relation extraction and
information
retrieval~\cite{west-2014-kbc-via-qa,riedel-2013-mf-universal-schema}.
We take the top 30 predictions from each system and manually annotate
whether they are correct, and use those annotations to compute the
average precision (AP) and reciprocal rank (RR) of each system on the
query.  Average precision is defined as $\frac{1}{m}\sum^m_{k=1}
\mathrm{Prec}(k) \times \mathrm{Correct}(k)$, where $\mathrm{Prec}(k)$
is the recision at rank $k$, $\mathrm{Correct}(k)$ is an indicator
function for whether the $k$th answer is correct, and $m$ is number of
returned answers (up to 100, in this evaluation).  Reciprocal rank is
computed by first finding the rank $r$ of the first correct prediction
made by a system.  Reciprocal rank is then $\frac{1}{r}$, ranging from
1 (if the first prediction is correct) to 0 (if there is no correct
answer returned).  In the tables below we report \emph{mean} average
precision (MAP) and reciprocal rank (MRR), averaged over all of the
queries in the test set.  We also report a weighted version of MAP,
where the AP of each query is scaled by the number of annotated
correct answers to the query (shown as W-MAP in the tables for space
considerations).

@@

\begin{table}
  \centering
  {\small
    \begin{tabular}{lcc}
      \toprule
      Method & K\&M's LFs & Our LFs \\
      \midrule
      Distributional-only & .269 & \textbf{.284} \\
      \midrule
      Formal-only & .231 & \textbf{.276} \\
      \midrule
      Combined model & .313 & \textbf{.335} \\
      \bottomrule
    \end{tabular}
  }
  \caption{Comparison of models using logical forms from prior work
  versus those introduced in this paper.  The metric shown is mean
  average precision on the dev set.  With our logical forms,
  performance of all models improves, quite substantially in the case
  of the formal model.}
  \label{tab:better-lfs}
\end{table}

@@

\begin{table}
  \centering
  {\small
    \begin{tabular}{lccc}
      \toprule
      Method & MAP & W-MAP & MRR \\
      \midrule
      Distributional model & .163 & .163 & .288 \\
      \midrule
      With freebase entities & .\textbf{229} & \textbf{.275} & \textbf{.312} \\
      \bottomrule
      Relative improvement & 40\% & 69\% & 8\% \\
      \bottomrule
    \end{tabular}
  }
  \caption{Allowing Krishnamurthy and Mitchell's model to propose
  candidate entities from Freebase improves mean average precision
  substantially, by allowing the model to have higher recall.}
  \label{tab:better-candidates}
\end{table}

@@

\begin{table}
  \centering
  {\small
    \begin{tabular}{lccc}
      \toprule
      Method & MAP & W-MAP & MRR \\
      \midrule
      Prior work (distributional) & .284 & .371 & .379 \\
      \midrule
      Our formal model & .276 & .469 & .334 \\
      \midrule
      Our combined model & \textbf{.335} & \textbf{.477} & \textbf{.429} \\
      \bottomrule
      Relative improvement & 18\% & 29\% & 13\% \\
      \bottomrule
    \end{tabular}
  }
  \caption{Results on the development set for our fill-in-the-blank task.  The
  combined model significantly improves MAP over prior work.}
  \label{tab:dev-results}
\end{table}

\tabref{dev-results} shows the results of our experiments on the
development set (the same as the test set used by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}).  As
can be seen, the combined model significantly improves performance,
giving a relative gain in weighted MAP of 29\%.

\begin{table}
  \centering
  {\small
    \begin{tabular}{lccc}
      \toprule
      Method & MAP & W-MAP & MRR \\
      \midrule
      Prior work (distributional) & .229 & .275 & .312 \\
      \midrule
      Our formal model & .355 & .495 & .419 \\
      \midrule
      Our combined model & \textbf{.370} & \textbf{.513} & \textbf{.469} \\
      \bottomrule
      Relative improvement & 62\% & 87\% & 50\% \\
      \bottomrule
    \end{tabular}
  }
  \caption{Results on the final test set for our fill-in-the-blank
  task.  The combined model improves over prior work by 50--87\% on
  our metrics.  Note that these improvements over the baseline are
  \emph{after} the baseline has been improved by the methods developed
  in this paper, shown in \tabref{better-lfs} and
  \tabref{better-candidates}.  The cumulative effect of the methods
  presented in this work is an improvement of over 120\% in MAP.}
  \label{tab:final-results}
\end{table}

@@

On both of these datasets, the difference in MAP between the combined
model and the distributional model is statistically significant (by a
paired permutation test, $p < 0.05$).  The difference between the
combined model and the formal model, and between the formal model and
the distributional model, are not statistically significant, as each
method has certain kinds of queries that it performs well on.  Only
the combined model is able to consistently outperform the
distributional model on all kinds of queries.

>>>>

\title{Open-Vocabulary Semantic Parsing\\with both Distributional
Statistics and Formal Knowledge}

@@

  We consider the problem of mapping language onto meaning
  representations that are executable, returning truth values for
  complete statements and distributions over entities for queries.
  The typical approach to solve this problem is semantic parsing;
  however, this approach fails when the language cannot be represented
  by a single query over the Freebase schema.  Instead, our approach
  represents language as a \emph{weighted combination} of queries over
  the formal schema, along with a distributional component similar to
  a word embedding.  This technique combines the advantages of
  traditional semantic parsing (compositionality and the ability to
  leverage a structured knowledge base) with the broad coverage
  obtained by distributional methods.  We present relative gains of
  over 120\% in mean average precision versus prior work on an
  open-vocabulary fill-in-the-blank question answering task.

@@

How should a computer program represent the meaning of a word or a
phrase? Recent work has suggested two vastly different
approaches---distributional vector space models and semantic
parsing---each with its own advantages and disadvantages. On one hand,
distributional models produce a vector representation of the meaning
of each word from a large unlabeled text corpus. These models have
broad coverage, but they also have a shallow semantics centered around
word similarity. On the other hand, semantic parsing translates
natural language into logical queries against a formal knowledge base,
such as Freebase. This approach produces a rich compositional
semantics and furthermore can leverage structured information from the
knowledge base. However, semantic parsers have limited coverage as
they can only represent the meanings of words that can be mapped to
knowledge base predicates. A critical question is \emph{how do we
obtain the benefits of both of these approaches?}

\begin{figure*}[ht]
  \small
  \begin{minipage}{0.18\linewidth}
    \textbf{Input Text}\\Italian architect \blank{}
  \end{minipage}
%
  ~~ $\longrightarrow$ ~~~~~~
%
  \begin{minipage}{0.7\linewidth}
    \textbf{Logical Form}\\
    $\lexicalpredicate{architect}(x)~\land~\lexicalpredicate{architect\_N/N}(\entity{Italy}, x)$
  \end{minipage}

@@

In this work, we introduce new models of predicate semantics that
leverage both structured information from Freebase and distributional
information from a corpus. Our key observation is that, while there is
no Freebase predicate that corresponds exactly to the meaning of
``honcho,'' Freebase \emph{does} contain predicates that
\emph{partially} represent its meaning. For example, an entity that
can be called ``honcho'' is likely to have type
\formalpredicate{person}. We therefore incorporate \emph{features}
based on Freebase paths into the predicate models of Krishnamurthy and
Mitchell and learn per-predicate weights for these features using
distributional information (\figref{overview}). This approach
effectively learns the meaning of a word as a distributional vector
plus a \emph{weighted combination of Freebase queries}, a considerably
more expressive representation than either traditional semantic parsers
or the work by Krishnamurthy and Mitchell.

We demonstrate our approach on the task of answering fill-in-the-blank
natural language queries.  We first present two simple improvements to
the distributional models of Krishnamurthy and Mitchell (an improved
surface logical form representation, and better candidate generation
during inference), improving the performance of that system by over
40\%.  We then show that our approach improves mean average precision
by 62\% over this improved baseline.  Taken together, the methods
presented in this paper give a relative gain over prior work of more
than 120\%.

@@

In this work, we make heavy use of the open-vocabulary semantic parser
of Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, as
well as features derived from a knowledge base using a technique
called subgraph feature extraction~\cite{gardner-2015-sfe}.  We
briefly describe both of these techniques.

@@

Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
introduced a technique for learning semantic parsers with open
predicate vocabularies. Instead of mapping text directly to Freebase
queries, this method parses text to a surface logical form whose
predicates are derived directly from the words in the text (an example
of these logical forms is shown in \figref{overview}). Next, a
distribution over denotations for each predicate is learned using a
matrix factorization approach similar to that of Riedel et
al.~\shortcite{riedel-2013-mf-universal-schema}. This distribution is
concisely represented using a probabilistic database, which also
enables efficient probabilistic execution of logical form queries.

The truth probability of a predicate instance such as
\lexicalpredicate{architect}(\entity{AndreaPalladio}) is learned using
probabilistic matrix factorization. This factorization has two sets of
parameters: each category or relation has a learned $k$-dimensional
embedding $\theta$, and each entity or entity pair has a learned
$k$-dimensional embedding $\phi$. The probability assigned to a
category instance $c(e)$ or relation instance $r(e_1, e_2)$ is given
by:

@@

In this paper, we use the open-vocabulary semantic parsing framework
outlined in this section.  However, where Krishnamurthy and Mitchell
used only distributional methods to compute $P(c(e))$ and $P(r(e_1,
e_2))$, we augment these models with features derived from a formal
knowledge base, as described in \secref{method}.

@@

    \path[]
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{nationality}} (2)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (3)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{designed}} (5)
      (2) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (4)
      (5) edge node [sloped, anchor=center, above] {\formalpredicate{located\_in}} (2);
  \end{tikzpicture}
  }
  \textbf{Features between \entity{Palladio} and \entity{Italy}}:\\
  \textless\formalpredicate{nationality}\textgreater\\
  \textless\formalpredicate{designed}$\rightarrow$\formalpredicate{located\_in}\textgreater
  \caption{A subset of the Freebase graph, and some example extracted
  features between \entity{Palladio} and \entity{Italy}.  The actual
  Freebase relations and entity identifiers used are modified here to
  aid readability.}
  \label{fig:sfe}
\end{figure}

Subgraph feature extraction (SFE) is a technique introduced by Gardner
and Mitchell~\shortcite{gardner-2015-sfe} for generating feature
matrices over node pairs in a graph with labeled edges.  Given a pair
of nodes in a graph, SFE performs a search to characterize and extract
features from a subgraph around those two nodes.  Example features
include the set of edge sequences that connect the two nodes.
\figref{sfe} shows an example subgraph for the pair \entity{Andrea
Pallado} and \entity{Italy}, and features that would be extracted for
that entity pair.  Gardner and Mitchell used these features to perform
link prediction in the graph, using characteristics of the subgraph
around two nodes to determine if an edge of a particular type should
exist between those nodes.\footnote{When the graph corresponds to a
knowledge base like Freebase, this task is also known as knowledge
base completion.}

We differ from the work done by Gardner and Mitchell in two ways.
First, we apply these features to models of natural language, instead
of to the link prediction task.  Second, Gardner and Mitchell only
considered generating feature matrices over node \emph{pairs} in a
graph, with which one can model binary relations.  The natural
language queries we wish to answer also involve unary predicates.  We
thus extend SFE to also generate feature matrices over \emph{nodes} in
a graph, a straightforward extension that is described in
\secref{method}.

@@

We evaluate our models of predicate semantics on a fill-in-the-blank
natural language query task.  Each test example is a natural language
phrase containing at least two Freebase entities, one of which is held
out.  The system must propose a ranked list of Freebase entities to
fill in the blank left by the held out entity, and the predicted
entities are then judged manually for correctness.  We compare our
proposed models, which combine distributional and formal elements,
with a purely distributional baseline from prior work.  All of the
data and code used in these experiments is available at [url withheld
for review].

@@

We also used the test set created by Krishnamurthy and Mitchell, which
contains 220 queries generated in the same fashion as the training
data from a separate section of ClueWeb.  However, as they did not
release a development set in with their data, we used this set as a
development set.  For a final evaluation, we generated another,
similar test set from a different held out section of ClueWeb, in the
same fashion as done by Krishnamurthy and Mitchell.  This final test
set contains 307 queries.  We report results on both of these sets
below.

@@

We compare three models in our experiments: (1) a distributional model
(the prior work of Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}); (2)
a formal model (new to this work), where the distributional parameters
$\theta$ and $\phi$ in \secref{formal-and-distributional} are fixed at
zero; and (3) the combined model described in
\secref{formal-and-distributional} (also new to this work).  Except
where noted, all experiments use our modified logical forms
(\secref{better-lfs}) and our entity proposal mechanism
(\secref{better-candidates}).

@@

Given a fill-in-the-blank query such as ``Italian architect
\blank{}'', each system produces a ranked list of 100 candidate
entities.  To compare the output of the systems, we follow a pooled
evaluation protocol commonly used in relation extraction and
information
retrieval~\cite{west-2014-kbc-via-qa,riedel-2013-mf-universal-schema}.
We take the top 30 predictions from each system and manually annotate
whether they are correct, and use those annotations to compute the
average precision (AP) and reciprocal rank (RR) of each system on the
query.  Average precision is defined as $\frac{1}{m}\sum^m_{k=1}
\mathrm{Prec}(k) \times \mathrm{Correct}(k)$, where $\mathrm{Prec}(k)$
is the precision at rank $k$, $\mathrm{Correct}(k)$ is an indicator
function for whether the $k$th answer is correct, and $m$ is number of
returned answers (up to 100 in this evaluation).  Reciprocal rank is
computed by first finding the rank $r$ of the first correct prediction
made by a system.  Reciprocal rank is then $\frac{1}{r}$, ranging from
1 (if the first prediction is correct) to 0 (if there is no correct
answer returned).  In the tables below we report \emph{mean} average
precision (MAP) and reciprocal rank (MRR), averaged over all of the
queries in the test set.  We also report a weighted version of MAP,
where the AP of each query is scaled by the number of annotated
correct answers to the query (shown as W-MAP in the tables for space
considerations).

@@

\begin{table}
  \centering
  {\small
    \begin{tabular}{lcc}
      \toprule
      Method & K\&M's LFs & Our LFs \\
      \midrule
      Distributional model & .269 & \textbf{.284} \\
      \midrule
      Formal model & .231 & \textbf{.276} \\
      \midrule
      Combined model & .313 & \textbf{.335} \\
      \bottomrule
    \end{tabular}
  }
  \caption{Comparison of models using logical forms from prior work
  versus those introduced in this paper.  The metric shown is mean
  average precision on the dev set.  With our logical forms,
  performance of all models improves, quite substantially in the case
  of the formal model.}
  \label{tab:better-lfs}
\end{table}

@@

\begin{table}
  \centering
  {\small
    \begin{tabular}{lccc}
      \toprule
      Method & MAP & W-MAP & MRR \\
      \midrule
      Distributional model & .163 & .163 & .288 \\
      \midrule
      With freebase entities & .\textbf{229} & \textbf{.275} & \textbf{.312} \\
      \midrule
      \midrule
      Relative improvement & 40\% & 69\% & 8\% \\
      \bottomrule
    \end{tabular}
  }
  \caption{Allowing Krishnamurthy and Mitchell's model to propose
  candidate entities from Freebase improves mean average precision
  substantially, by allowing the model to have higher recall.}
  \label{tab:better-candidates}
\end{table}

@@

\begin{table}
  \centering
  {\small
    \begin{tabular}{lccc}
      \toprule
      Method & MAP & W-MAP & MRR \\
      \midrule
      Prior work (distributional) & .284 & .371 & .379 \\
      \midrule
      Our formal model & .276 & .469 & .334 \\
      \midrule
      Our combined model & \textbf{.335} & \textbf{.477} & \textbf{.429} \\
      \midrule
      \midrule
      Relative improvement & 18\% & 29\% & 13\% \\
      \bottomrule
    \end{tabular}
  }
  \caption{Results on the development set for our fill-in-the-blank task.  The
  combined model significantly improves MAP over prior work.}
  \label{tab:dev-results}
\end{table}

\tabref{dev-results} shows the results of our experiments on the
development set.  As can be seen, the combined model significantly
improves performance over prior work, giving a relative gain in
weighted MAP of 29\%.

\begin{table}
  \centering
  {\small
    \begin{tabular}{lccc}
      \toprule
      Method & MAP & W-MAP & MRR \\
      \midrule
      Prior work (distributional) & .229 & .275 & .312 \\
      \midrule
      Our formal model & .355 & .495 & .419 \\
      \midrule
      Our combined model & \textbf{.370} & \textbf{.513} & \textbf{.469} \\
      \midrule
      \midrule
      Relative improvement & 62\% & 87\% & 50\% \\
      \bottomrule
    \end{tabular}
  }
  \caption{Results on the final test set for our fill-in-the-blank
  task.  The combined model improves over prior work by 50--87\% on
  our metrics.  Note that these improvements over the baseline are
  \emph{after} the baseline has been improved by the methods developed
  in this paper, shown in \tabref{better-lfs} and
  \tabref{better-candidates}.  The cumulative effect of the methods
  presented in this work is an improvement of over 120\% in MAP.}
  \label{tab:final-results}
\end{table}

@@

On both of these datasets, the difference in MAP between the combined
model and the distributional model is statistically significant (by a
paired permutation test, $p < 0.05$).  The differences between the
combined model and the formal model, and between the formal model and
the distributional model, are not statistically significant, as each
method has certain kinds of queries that it performs well on.  Only
the combined model is able to consistently outperform the
distributional model on all kinds of queries.
